
    \begin{conf-abstract}[]
        {\textbf{A Survey on Wireless Sensor Network Routing Performance Optimizing and Security Techniques}}
        {\textit{Anindya Nag$^{1}$, Nisarga Chand$^{2}$, Dishari  Mandal$^{3,Nilanjana  Roy4}$, SM Firoz Ahmed  Fahim$^{5}$}}
        {$^{1}$Khulna University $\bullet$ $^{2}$Adamas University $\bullet$ $^{3}$Adamas University $\bullet$ $^{4}$Adamas University $\bullet$ $^{5}$AIUB}
        {\texttt{anindyanag58@gmail.com, nisargaece@gmail.com, disharimandal5@gmail.com, nilanjanaroy524@gmail.com,  firozfahimm@gmail.com}}
        \indexauthors{Nag!Anindya, Chand!Nisarga, Mandal!Dishari , Fahim!SM Firoz Ahmed }
        {Wireless Sensor Network (WSN) is a contemporary topic of research that has proven to be an advantageous technology for a wide variety of applications, including those dealing with the environment, the military, health, as well as uses at home and in the workplace. There are two different kinds of WSNs: mobile WSN and static WSN. Distribution, location, and tracking are three of the many new conceptual and optimization challenges presented by WSNs. These challenges are particularly important given, the fact that a great number of applications are dependent on WSNs for information. There are a number of challenges associated with this type of WSN, including high bandwidth requirements, high energy consumption, the providing of Quality of Service (QoS), data processing, compression, and cross-layer design. Authors of this review have conducted a survey of the relevant literature and draw the conclusion that routing protocols for WSNs make use of a variety of approaches, such as Hierarchical Based Routing Protocols (HBRP) and Location-Based Routing Protocols (LBRP), in order to accomplish their goals. Each of these approaches is capable of meeting the necessary trans-mission specifications. The fundamental goal of the analysis is to ensure that both power consumption and security are taken into account while conducting the analysis of performance matrices.}
    \end{conf-abstract}
        