
    \begin{conf-abstract}[]
        {\textbf{Coverless Steganography: A Comprehensive Study on Concealing Data without a Cover Medium}}
        {\textit{Pabak Indu$^{1}$, Mousumi Dutta$^{2}$, Parichay Nandi$^{3}$, Nabajyoti Mazumdar$^{4}$, Souvik Bhattacharyya$^{5}$}}
        {$^{1}$Institute of Engineering and Management $\bullet$ $^{2}$Adamas University $\bullet$ $^{3}$Adamas University $\bullet$ $^{4}$IIIT Allahabad $\bullet$ $^{5}$University Institute of Technology}
        {\texttt{pabakindu@yahoo.co.in, mousumid721@gmail.com, pnandi2001@gmail.com, nabajyoti@iiita.ac.in, souvik.bha@gmail.com}}
        \indexauthors{Indu!Pabak, Dutta!Mousumi, Nandi!Parichay, Mazumdar!Nabajyoti, Bhattacharyya!Souvik}
        {This study examines the concept of coverless steganography, a method employed for the purpose of concealing information without relying on a traditional cover medium. This statement underscores the importance of information security in protecting sensitive data and mitigating cyber threats. The study categorises steganography into distinct domains, namely text, image, audio, and video, and investigates their respective methodologies, benefits, and constraints. The objective of this study is to establish a thorough comprehension of these methodologies. The topic of coverless steganography is also examined in this study. This technique involves the fragmentation of information into smaller units and their dispersion across multiple sources. The process of reconstructing the original information is facilitated through the utilisation of a shared key or algorithm. The literature review critically examines prior scholarly investigations, encompassing studies on synthetic coatings and the transmission pathways of encoding. The technique of coverless image steganography is notable for its ability to withstand steganalysis techniques. The resolution under consideration integrates coverless image steganography and AES encryption as a means to augment data security.  In conclusion, this research makes a valuable contribution to the comprehension of coverless steganography and its implications for the secure transmission of data. It enhances our understanding of information security and proposes potential directions for future exploration.}
    \end{conf-abstract}
        