
    \begin{conf-abstract}[]
        {\textbf{AI Based Criminal Detection and Tracking system for public safety and security}}
        {\textit{Jamuna S Murthy$^{1}$, Siddesh$^{2}$}}
        {$^{1}$Ramaiah Institute of Technology $\bullet$ $^{2}$MSRIT}
        {\texttt{jamunamurthy.s@gmail.com, siddeshgm14@gmail.com}}
        \indexauthors{Murthy!Jamuna S, Siddesh!}
        {The rise of criminal activities in public spaces has created a need for an efficient and reliable system that can detect, recognize, and track criminals. To address this need, an AI-based criminal detection, recognition, and tracking system has been proposed that can enhance public safety and security. The system automates the manual task of detecting and recognizing criminals, providing law enforcement agencies with a reliable and efficient tool to prevent and solve crimes. Proposed system leverages a novel Convolutional Neural Network (CNN) architecture called "CriminalNet-228 "to detect and recognize criminal faces in CCTV camera footage. CriminalNet-228 is trained on a large dataset of criminal images to increase the accuracy of the system. To improve the performance of face detection and acknowledge parallel processing and distributed computing is used additional computing resources. This allows the system to analyze vast amounts of CCTV footage simultaneously, which is not possible for humans to do in real-time. The system tracks the movements of recognized criminals using a map, providing law enforcement officials with real-time information to take appropriate action. The proposed CriminalNet-228 architecture has achieved an overall Mean Average Precision of of 0.65. The model is able to detect the faces of size as small as 4*4. }
    \end{conf-abstract}
        