
    \begin{conf-abstract}[]
        {\textbf{Multispectral imaging of Damaged Sacramental Journal pages: A preliminary study}}
        {\textit{Ankan Bhattacharyya$^{1}$, Clifford Seth Parker$^{2}$, William Brent Seales$^{3}$}}
        {$^{1}$University of Kentucky $\bullet$ $^{2}$University of Kentucky $\bullet$ $^{3}$University of Kentuck}
        {\texttt{ankan.bhattacharyya@uky.edu, c.seth.parker@uky.edu, seales@uky.edu}}
        \indexauthors{Bhattacharyya!Ankan, Parker!Clifford Seth, Seales!William Brent}
        {Multispectral Imaging (MSI) was used to recover the Archimedes Palimpsest. However, the work did not report to have any ink bleedthrough. We develop an MSI pipeline that helps in visualizing the content and the ink bleed-through. As for data, we use damaged pages from the sacramental journal of the Holy Trinity Greek Orthodox Community (HTGOC) Church, situated in New Orleans. During Hurricane Katrina, this church faced destruction leading to damaged sacramental journals, like ink wash-away, ink bleed-through, torn patches of pages, and mold development. In this work, we try to discover any ink signals that show up in a wide spectrum of light, from ultraviolet (UV) to infrared (IR). We also try to study the ink signal response to the different combination of wavelengths and perform an ablation study that gives us a list of combinations of different spectral bands that generates maximum information about the data. The manuscript reports 12 such combinations after the ablation study, and our data use all the wavelengths to produce ink signals, which are in better contrast in comparison to the images captured under visible light.}
    \end{conf-abstract}
        