
    \begin{conf-abstract}[]
        {\textbf{SSANet: Side-by-side Additive Network for Knee Osteoarthritis Severity Detection from X-ray Images}}
        {\textit{Hiranmoy Roy$^{1}$, Debotosh Bhattacharjee$^{2}$, Ondrej Krejcar$^{3}$, Rakhi Tewari$^{4}$}}
        {$^{1}$RCC Institute of Information Technology $\bullet$ $^{2}$JU $\bullet$ $^{3}$University of Hradec Kralove $\bullet$ $^{4}$ju}
        {\texttt{hiranmoy.roy@rcciit.org.in, debotoshb@hotmail.com, ondrej.krejcar@uhk.cz, rtewari4891@gmail.com}}
        \indexauthors{Roy!Hiranmoy, Bhattacharjee!Debotosh, Krejcar!Ondrej, Tewari!Rakhi}
        {Knee Osteoarthritis (KOA) is becoming one of the most frequent degenerative and irreversible diseases in elderly people. Its early detection and diagnosis is also a difficult and time-intensive task. The recent advance in Machine Learning (ML) and Computer Vision (CV) created new paths to automatically detect KOA in the early stages. Detecting and grading the severity of KOA requires a dedicated ML model. This paper proposes a Side-by-Side Additive Network (SSANet) based model for detecting and grading the severity of KOA. Since KOA affects the knee joint space by narrowing the gap between the joint, we preprocess the X-ray images to detect the Region of Interest (ROI) before the training of the model. Experimental results show that the ROI selection is really improving the detection accuracy of the model. Unlike sequentially connected convolution layer-based deep learning models, the proposed SSANet is based on a parallel convolution layer to reduce the degradation of feature quality. Again, to enhance the edge feature maps, we apply an additive layer that couples the previous layers' convolutional output. SSANet captures both low-level and high-level features to predict the KOA severity effectively. The presence of a smaller number of layers and fewer numbers of learnable parameters than the existing popular deep learning models, make SSANet a time and space-efficient network. Moreover, the performance of the proposed SSANet in detecting KOA severity is significantly better than that of other popular state-of-the-art networks.}
    \end{conf-abstract}
        