
    \begin{conf-abstract}[]
        {\textbf{A Real-Time Video Surveillance based framework for early plant disease detection using Jetson TX1 and novel LeafNet-104 algorithm}}
        {\textit{Jamuna S Murthy$^{1}$, Siddesh g$^{2}$}}
        {$^{1}$Ramaiah Institute of Technology $\bullet$ $^{2}$MSRIT}
        {\texttt{jamunamurthy.s@gmail.com, siddeshgm14@gmail.com}}
        \indexauthors{Murthy!Jamuna S, g!Siddesh}
        {The accurate and timely detection of plant diseases is crucial for ensuring crop health and optimizing agricultural yields. This paper presents a novel framework for plant disease detection using video surveillance-based cameras deployed on an Nvidia Jetson TX1 hardware platform in agricultural farms. The framework leverages the power of deep learning and the novel neural network architecture called LeafNet-104 algorithm to perform real-time disease detection on plants. By employing video surveillance cameras, continuous monitoring and early detection of diseases can be achieved, allowing farmers to take prompt remedial actions and prevent further damage to crops. The Nvidia Jetson TX1, with its high-performance computing capabilities, facilitates on-device processing, making it suitable for real-time applications. To evaluate the effectiveness of the proposed framework, experiments were conducted on a real agricultural farm. The dataset consisted of a variety of plant species and diseases. The accuracy, precision, recall, and F1-score were used as evaluation metrics to measure the performance of the LeafNet-104 algorithm. The experimental results demonstrated the framework's ability to accurately detect and classify plant diseases in real-time with 97.5\% accuracy rate.}
    \end{conf-abstract}
        